Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-10 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Small tweaks

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_2pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2021})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity

@@

\begin{frame}
\frametitle{Typical Training Program}
Stylized facts on MSME trainings
\begin{itemize_2pt}
	\item Group of 15 to 40 entrepreneurs per trainer
	\item In-class (often with elements of active and interactive learning)
	\item Period of up to two weeks	
	\item Foci of typical syllabi
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Encourage start-up}: Business ideas and business plans, permits, costing, pricing, and budgeting
		\item \textcolor{bdf}{Grow existing businesses}: Record-keeping, accounting, and financial planning, marketing, human resources and hiring, stock and inventory management
	\end{itemize_2pt}

	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{vanLieshout2017})
	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
	\item[] \quad (Median contribution 10\% of full price)

@@

\begin{itemize_2pt}
	\item Demand curve for business training in Jamaica: $\sim$60-70\% willing to pay half, $\sim$10\% full price \citep{Maffioli2020}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Impact on Performance}
First wave of evaluations
	\begin{itemize_2pt}
	\item  Headline result: \textcolor{bdf}{No impact on business performance}
	\begin{itemize_2pt}
		\item Modest short-term adoption of practices (long-term fade-out)
		\item Null-effect on business sales and profits
		\item Early examples: \citet{Field2010, Karlan2011, Bruhn2013}, also \citet[][WP in 2014]{Gine2021}

@@

Econometric and implementation issues \citep{McKenzie2014}
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Lack of statistical power} with MDEs often substantially above policy-relevant levels
		\begin{itemize_2pt}	
			\item Small samples (typically $N=200-400$ per treatment cell)
			\item Typical attendance between 40 and 70\%
			\item Typically substantial rates of survey attrition (up to $24-28\%$)
			\item Large heterogeneity in age, education, training delivery and costs, etc.
		\end{itemize_2pt}

@@

		\item Endline follow-ups \textcolor{bdf}{very short-term} (typically 1-2 years out)

@@

		\item Most trainings offered at \textcolor{bdf}{no private costs}
		\begin{itemize_2pt}
			\item Potential for reverse sunken cost fallacy in valuation \citep[see,][]{Maffioli2020}
		\end{itemize_2pt}

@@

		\item Structural reasons
		\begin{itemize_2pt}
			\item Women overrepresented in subsistence entrepreneurship
			\item Female entrepreneurs often subject to more severe constraints; e.g., due to household-level reallocation \citep[see, e.g.,][]{Bernhardt2019, deMel2009a}
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as \textcolor{bdf}{entrepreneurship courses in school or university} (business concepts and soft skills)
		\item Example: Final year university course in Tunisia \citep{Alaref2020}
		\begin{itemize_2pt}
			\item Positive impact on business entry tapers off after 4 years
		\end{itemize_2pt}
	\end{itemize_2pt}

@@

High-growth businesses ("gazelles")
\begin{itemize_2pt}
	\item Extensive-margin prediction of future MSE growth is hard \citep{Fafchamps2017}
	\begin{itemize_2pt}
		\item Survey, ability measure, expert panel all explain unique variation
		\item But: Business training for predicted gazelles shows no impact
	\end{itemize_2pt}

	\item \citet{McKenzie2017a} finds more encouraging results with a nationwide business plan competition in Nigeria

	\item Small literature on business accelerators and incubators
	\begin{itemize_2pt}
		\item \citet{Cusolito2021, GonzalezUribe2018, GonzalezUribe2021}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

Training of specific clusters of practices
\begin{itemize_2pt}	
	\item \citet{Anderson2018} assign 852 South African micro-entrepreneurs to two distinct trainings:

@@

		\item Marketing/sales skills
		\begin{itemize_2pt}
			\item "Growth focus" on higher sales, stock investments, and hiring
			\item 61\% increase in profits
			\item[] $\rightarrow$ Benefits new businesses ($=$ less market exposure)
		\end{itemize_2pt}

@@

		\begin{itemize_2pt}
			\item "Efficiency focus" on lower costs
			\item 41\% increase in profits
			\item[] $\rightarrow$ Benefits established businesses
		\end{itemize_2pt}

@@

	\item Typically one-on-one (also group-based)

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %[citation]Karlan2015, Bruhn2019
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically $\sim$10\%) \\
	\begin{itemize_2pt}
		%\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
	\end{itemize_2pt}

@@

Example: Subsidized matching grant program for MSMEs in Mexico \citep{Bruhn2018}
\begin{itemize_2pt}

@@

	\item Using admin data, \textcolor{bdf}{57\% higher employment after 5 years}
	\begin{itemize_2pt}
		\item Availability issues of admin data may have introduced selection
		\item Not clear if effects concentrated among few businesses
	\end{itemize_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Multimedia delivery}
TV shows
\begin{itemize_2pt}
	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \citep{Bjorvatn2020} and Egypt \citep{Barsoum2018}
	\item Differential random incentivization schemes
	\item[] $\rightarrow$ No impact on business knowledge and business entry 
	\item[] $\rightarrow$ But: \textcolor{bdf}{High viewership} (conventional MDEs substantially above policy-relevant levels)

@@

Text messages
\begin{itemize_2pt}
	\item Examples: 
	\begin{itemize_2pt}
		\item Heuristics-based business advice \citep{Cole2018}
		\item Daily personalized inventory level recommendations \citep{Acimovic2020}
	\end{itemize_2pt}
	\item[] $\rightarrow$ Small literature with generally \textcolor{camel}{mixed results or null effects}
	\item[] $\rightarrow$ But: \textcolor{bdf}{MDEs substantially above policy-relevant levels}
	\item[] $\rightarrow$ But: \textcolor{bdf}{Complementarities} between in-person training and SMS reminders still unclear
\end{itemize_2pt}
\end{frame}

@@

Alternative measures of business profits \citep{deMel2009}
	\begin{itemize_2pt}
		\item 15-16 unannounced visits during one month
		\item Random assignment of profit measure, and accounting diaries, and recall span
	\end{itemize_2pt}

@@

	\begin{enumerate_2pt}
		\item \textcolor{bdf}{Self-reported profits most accurate measure}
		\item[] $\rightarrow$ Correlation with sales-minus-expenditures only $r=0.3$
		\item \textcolor{bdf}{Accounting diaries have no effect on profits} (but on sales)
		\item With recall over 4 months vs. 1 month, entrepreneurs \textcolor{bdf}{understate revenues by $10 - 15 \%$ due to memory} 
		\item Entrepreneurs estimate average rival business to \textcolor{bdf}{underreport sales by 30\%}
	\end{enumerate_2pt}

@@

Survey media and frequencies \citep{Garlick2019}
\begin{itemize_2pt}
	\item 12-week panel with detailed measurements of employees, profits, sales, assets, transfers, etc.
	\item Random assignment to different survey modes and frequencies
	\begin{enumerate_2pt}
		\item Monthly in-person
		\item Weekly in-person
		\item Weekly phone
	\end{enumerate_2pt}

@@

	\item Survey medium
	\begin{itemize_2pt}
		\item \textcolor{bdf}{All survey modes generally yield similar statistical moments}
		\item Phone surveys yield higher within-firm, cross-temporal variation
		\item[] (Some evidence for greater social desirability bias.)
	\end{itemize_2pt}

@@

	\item \textcolor{bdf}{Vast majority of large changes in sales and profits genuine income volatility}
	\item Positive, but limited, effect of consistency checks in reducing variation in firm performance (and within-firm autocorrelation)

@@

\begin{itemize_2pt}
	\item Typical small-firm owner dropped out of highschool
	\item Test scores on digitspan and Raven's matrices about \% of Western university samples \textcolor{red}{\citep[comp.][]{}}
\end{itemize_2pt}
\end{frame}

@@

Family commitments
\begin{itemize_2pt}
	\item \textcolor{bdf}{Unequal responsibilities for child care} \citep[see, e.g.,][]{Delecourt2021}
	\begin{itemize_2pt}
		\item Audit study with mystery shoppers among drug stores in Uganda
		\item Average gender profit gap of 60\%
		\item Close to all women have $\geq$ 1 child, breastfeed for median 19.8 months
		\item[] $\rightarrow$ Among female entrepreneurs, those with child at work ..
		\begin{itemize_2pt}
			\item .. are \textcolor{bdf}{out of stock} more often, and stock up less.
			\item .. have \textcolor{bdf}{48\% lower profits}.
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

Market segregation
\begin{itemize_2pt}
	\item Markets can be geographically (and socially) segregated, especially in residential areas
	\begin{itemize_2pt}
		\item Potential \textcolor{bdf}{demand constraints} \citep[in the spirit of][, for women in Ghana]{Hardy2020}
		\item (Scant work, but seems important.)
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

@@

	\item In theoretical work, aspirations are modeled as \textcolor{bdf}{reference-dependent preferences}
	\begin{itemize_2pt}
		\item Agent derives utility from relative level wrt their aspirations
		\item[] $\rightarrow$ Aspirations motivate effort
		\item Behavioral constraint: \textcolor{bdf}{Agent neglects outcomes $\rightarrow$ aspirations}
	\end{itemize_2pt}

@@

	\item Consequence: Sufficiently \textcolor{bdf}{poor agent} with sufficiently \textcolor{bdf}{low aspirations} chooses \textcolor{bdf}{suboptimally low effort}
	\item[] $\rightarrow$ Potential for behavioral poverty trap
	\vspace{0.1in}

@@

	\item \href{https://www.poverty-action.org/study/impact-cash-transfers-aspirations-and-goal-setting-economic-outcomes-and-well-being}{Garlick et al. (in progress)} cross-randomize role-model intervention and large UCT to study complementarity
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Exposure to role models increases aspirations, labor supply, expenditures, and sales}
		\item Cash also increases aspirations, labor supply, expenditures, and sales
	\end{itemize_2pt}

@@

	\item Aspiration interventions can backfire
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citep[see also,][]{Galiani2018}
	\end{itemize_2pt}

>>>>

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_2pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} \citep[for $\sim$ 4-5 million entrepreneurs;][]{McKenzie2021}
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity

@@

\begin{frame}
\frametitle{Typical Training Program}
Stylized facts on MSME trainings
\begin{itemize_2pt}
	\item Group of 15 to 40 entrepreneurs per trainer
	\item \textcolor{bdf}{In-class} (may incl elements of active and interactive learning)
	\item Period of up to two weeks	
	\item Foci of typical syllabi
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Encourage start-up}: Business ideas and business plans, permits, costing, pricing, and budgeting
		\item \textcolor{bdf}{Grow existing businesses}: Record-keeping, accounting, and financial planning, marketing, human resources and hiring, stock and inventory management
	\end{itemize_2pt}

	\item Average training program not inexpensive \citep[USD 177 per person for ILO training;][]{vanLieshout2017}
	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
	\item[] \quad (Median contribution 10\% of full price)

@@

\begin{itemize_2pt}
	\item Demand curve for business training in Jamaica: \textcolor{bdf}{$\sim$10\% willing to pay full price}, $\sim$60-70\% half  \citep{Maffioli2020}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Impact on Performance}
First wave of evaluations
	\begin{itemize_2pt}
	\item  Headline result: \textcolor{bdf}{No impact on business performance}
	\begin{itemize_2pt}
		\item Modest short-term adoption of practices (long-term fade-out)
		\item Null-effect on business sales and profits
		\item Early examples: \citet{Field2010, Karlan2011, Bruhn2013}; also \citet[][WP in 2014]{Gine2021}

@@

Econometric and implementation issues \citep{McKenzie2014}
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Lack of statistical power} with MDEs often substantially above policy-relevant levels
		\begin{itemize_2pt}	
			\item Small samples (typically $N=200-400$ per treatment cell)
			\item Typical attendance between 40 and 70\%
			\item Often substantial rates of survey attrition (up to $24-28\%$)
			\item Large heterogeneity in age, education, training delivery and costs, etc.
		\end{itemize_2pt}

@@

		\item \textcolor{bdf}{Endline follow-ups typically short-term} (typically 1-2 years out)

@@

		\item Most trainings offered at \textcolor{bdf}{no private costs}
		\begin{itemize_2pt}
			\item Potentially lower valuation, utilization \citep[see,][]{Maffioli2020}
		\end{itemize_2pt}

@@

		\item Structural reasons
		\begin{itemize_2pt}
			\item Women overrepresented in mere subsistence entrepreneurship
			\item Female entrepreneurs often subject to more severe constraints
			\item[] \citep[e.g., due to household-level reallocation; see][]{Bernhardt2019, deMel2009a}
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as \textcolor{bdf}{entrepreneurship courses in school or university} (business concepts and soft skills)
		\item Example: Final year university course in Tunisia \citep{Alaref2020}
		\begin{itemize_2pt}
			\item Initial positive impact on business entry
			\item[] $\rightarrow$ \textcolor{bdf}{Effects taper off after 4 years} (no evidence for lasting effects)
		\end{itemize_2pt}
	\end{itemize_2pt}

@@

High-growth businesses ("gazelles")
\begin{itemize_2pt}
	\item Extensive-margin prediction of future MSE growth is hard \citep{Fafchamps2017}
	\begin{itemize_2pt}
		\item Survey, ability measure, expert panel all explain unique variation
		\item But: \textcolor{bdf}{Business training for predicted gazelles shows no impact}
	\end{itemize_2pt}

	\item \citet{McKenzie2017a} finds \textcolor{bdf}{more encouraging results with a large-scale, high-stakes business plan competition} in Nigeria

	\item Small literature on business accelerators and incubators
	\begin{itemize_2pt}
		\item See, e.g., \citet{Cusolito2021, GonzalezUribe2018, GonzalezUribe2021}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

Training of specific clusters of practices
\begin{itemize_2pt}	
	\item \citet{Anderson2018} vary \textcolor{bdf}{training focus} among 852 South African micro-entrepreneurs

@@

		\item Marketing/sales skills
		\begin{itemize_2pt}
			\item \textcolor{bdf}{"Growth focus" on higher sales, stock investments, and hiring}
			\item 61\% increase in profits
			\item[] $\rightarrow$ Benefits new businesses ($=$ less market exposure)
		\end{itemize_2pt}

@@

		\begin{itemize_2pt}
			\item \textcolor{bdf}{"Efficiency focus" on lower costs}
			\item 41\% increase in profits
			\item[] $\rightarrow$ Benefits established businesses
		\end{itemize_2pt}

@@

	\item Typically one-on-one \citep[also group-based; see,][]{McKenzie2021b}

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %[citation]Karlan2015, Bruhn2019
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{bdf}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically $\sim$10\%) \\
	\begin{itemize_2pt}
		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
	\end{itemize_2pt}

@@

Example: Matching grant program for MSMEs in Mexico \citep{Bruhn2018}
\begin{itemize_2pt}

@@

	\item Using admin data, \textcolor{bdf}{57\% higher employment after 5 years}
	\begin{itemize_2pt}
		\item Limited availability of admin data may introduce \textcolor{bdf}{selection bias}
		\item Not clear if effects concentrated among few businesses
	\end{itemize_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Multimedia delivery}
TV shows
\begin{itemize_2pt}
	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \citep{Bjorvatn2020} and Egypt \citep{Barsoum2018}
	\item Differential random incentivization schemes
	\item[] $\rightarrow$ \textcolor{bdf}{No impact} on business knowledge and business entry 
	\item[] $\rightarrow$ But: \textcolor{bdf}{High viewership} (conventional MDEs substantially above policy-relevant levels)

@@

Text messages
\begin{itemize_2pt}
	\item Examples: 
	\begin{itemize_2pt}
		\item Heuristics-based business advice \citep{Cole2018}
		\item Personalized inventory recommendations \citep{Acimovic2020}
	\end{itemize_2pt}
	\item[] $\rightarrow$ Small literature with generally \textcolor{bdf}{mixed results or null effects}
	\item[] $\rightarrow$ But: \textcolor{bdf}{Extremely cheap} (MDEs above policy-relevant levels)
	\item[] $\rightarrow$ But: \textcolor{bdf}{Potential complementarities} with in-person training
\end{itemize_2pt}
\end{frame}

@@

Alternative measures of business profits \citep{deMel2009}
	\begin{itemize_2pt}
		\item 15-16 unannounced visits during one month
		\item Random assignment of profit measure, accounting diaries, and recall span
	\end{itemize_2pt}

@@

	\begin{enumerate_2pt}
		\item \textcolor{bdf}{Self-reported profits most accurate measure}
		\item[] $\rightarrow$ Correlation with sales-minus-expenditures only $r=0.3$
		\item \textcolor{bdf}{Accounting diaries have no effect on profits} (but on sales)
		\item With recall over 4 months vs. 1 month, entrepreneurs \textcolor{bdf}{understate revenues by $10 - 15 \%$ due to memory loss} 
		\item Entrepreneurs estimate average rival business to \textcolor{bdf}{underreport sales by 30\%}
	\end{enumerate_2pt}

@@

Survey media and frequencies \citep{Garlick2019}
\begin{itemize_2pt}
	\item 12-week panel with detailed measurements of employees, assets, profits, sales, transfers, etc.
	\item Random assignment to different survey modes and frequencies
	\begin{enumerate_2pt}
		\item Monthly in-person
		\item Weekly in-person
		\item Weekly phone
	\end{enumerate_2pt}

@@

	\item Survey medium
	\begin{itemize_2pt}
		\item \textcolor{bdf}{All survey modes generally result in similar statistical moments}
		\item Phone surveys yield higher within-firm variation
		\item[] (And may be more vulnerable to social desirability bias.)
	\end{itemize_2pt}

@@

	\item Key result: \textcolor{bdf}{Vast majority of large changes in sales and profits genuine income volatility}
	\begin{itemize_2pt}
		\item Positive, but limited, effect of consistency checks in reducing variation in firm performance
	\end{itemize_2pt}

@@

\begin{itemize_2pt}
	\item Typical micro-entrepreneur is a high-school dropout
	\item Test scores on digitspan and Raven's matrices about \% of Western university samples \textcolor{red}{\citep[comp.][]{}}
\end{itemize_2pt}
\end{frame}

@@

Family commitments
\begin{itemize_2pt}
	\item \textcolor{bdf}{Unequal responsibilities for child care} \citep{Delecourt2021}
	\begin{itemize_2pt}
		\item Audit study with mystery shoppers among drug stores in Uganda
		\item Average gender profit gap of 60\%
		\item Close to all women have $\geq$ 1 child, breastfeed for median 19.8 months
		\item[] $\rightarrow$ Among female entrepreneurs, those with child at work ..
		\begin{itemize_2pt}
			\item .. are \textcolor{bdf}{out of stock} more often, and stock up less.
			\item .. have \textcolor{bdf}{48\% lower profits}.
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

Market segregation
\begin{itemize_2pt}
	\item Markets can be geographically (and socially) segregated, especially in residential areas
	\begin{itemize_2pt}
		\item Potential \textcolor{bdf}{demand constraints} \citep[in the spirit of][studying women in Ghana]{Hardy2020}
		\item (Scant work, but seems important.)
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

@@

	\item In theoretical work, aspirations are modeled as \textcolor{bdf}{reference-dependent preferences}
	\begin{itemize_2pt}
		\item Agent derives utility from relative level wrt aspirations
		\item[] $\rightarrow$ Aspirations motivate effort
		\item Behavioral constraint: \textcolor{bdf}{Agent neglects outcomes $\rightarrow$ aspirations}
	\end{itemize_2pt}

@@

	\item Consequence: Sufficiently \textcolor{bdf}{poor agents} with sufficiently \textcolor{bdf}{low aspirations} choose suboptimally low effort
	\item[] $\rightarrow$ Potential for \textcolor{bdf}{behavioral poverty trap}
	\vspace{0.1in}

@@

	\item \href{https://www.poverty-action.org/study/impact-cash-transfers-aspirations-and-goal-setting-economic-outcomes-and-well-being}{Garlick et al. (in progress)} cross-randomize role-model intervention and large UCT to study complementarity
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Exposure to role models increases aspirations, labor supply, expenditures, and sales}
		\item[] (Cash also increases aspirations, labor supply, expenditures, and sales.)
	\end{itemize_2pt}

@@

	\item \textcolor{bdf}{Aspiration interventions can backfire}
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citep[see also,][]{Galiani2018}
	\end{itemize_2pt}
